Visual Diagnostics of a Model Explainer -- Tools for the Assessment of LIME Explanations

### 2020-09-11 README.Rmd
removed NA from test data

- Remove NAs from test data
- Write cover letter
- Finish filling in questions in ASA submission document
- Figure out discrepancies with old and new versions of the training data
- Rerun the lime explanations with the finalized training data
- Edit dataset descriptions in README and add to the readme.txt document for submission
- Update all files in the submission folder
- Upload the files for submission and submit
- Look into using renev

>>>>

- Write cover letter
- Finish filling in questions in ASA submission document
- Figure out discrepancies with old and new versions of the training data
- Rerun the lime explanations with the finalized training data
- Edit dataset descriptions in README and add to the readme.txt document for submission
- Update all files in the submission folder
- Upload the files for submission and submit
- Look into using renev
